%% -----------------------------------------------------------------------------
%% MIT License
%%
%% Copyright 2025 ThirtySomething
%%
%% Permission is hereby granted, free of charge, to any person obtaining a
%% copy of this software and associated documentation files (the "Software"),
%% to deal in the Software without restriction, including without limitation
%% the rights to use, copy, modify, merge, publish, distribute, sublicense,
%% and/or sell copies of the Software, and to permit persons to whom the
%% Software is furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included
%% in all copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS
%% OR IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL
%% THE AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING
%% FROM, OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER
%% DEALINGS IN THE SOFTWARE.
%% -----------------------------------------------------------------------------

%% -----------------------------------------------------------------------------
%% Motivation for the document
%% -----------------------------------------------------------------------------

\section{Motivation}

In den letzten Jahren ist die elektronische Verarbeitung von Daten immer
wichtiger geworden. Es werden immer mehr Dokumente verfasst. Daraus ergeben
sich wichtige Fragen, deren Beantwortung hilft, einen Datenverlust zu vermeiden.

\begin{itemize}
    \item[1.] Wie sollen die Daten organisiert werden?
    \item[2.] Wie können die Daten gesichert werden?
    \item[3.] Ist es möglich, die zeitlich verschiedene Versionen eines Dokumentes
          vorzuhalten?
\end{itemize}

Zu 1. wird in diesem Dokument nicht eingegangen. Hintergrund ist, dass die
Organisation der Daten stark vom jeweiligen Einsatzzweck abhängig ist. Unter
Umständen sind gesetzliche Vorgaben zu beachten. Möglicherweise gibt es in
einer Firma spezielle Richtlinien, die eingehalten werden müssen. Die
persönlichen Vorlieben spielen ebenfalls eine Rolle. Daher ist es nicht
möglich, eine allgemeingültige Aussage hierzu zu treffen.
\bigskip

Die anderen Punkte werden im folgenden Konzept behandelt, da die Themen
unabhängig von der Dateiablage sind und somit allgemeingültig abgehandelt
werden können.
